---
title: "TeenTee: Pre-Post Comparison"
shorttitle: "Final Research Project"
author:
  - name: Mehak Madan
    corresponding: true
    email: mehakmadan@uchicago.edu
    affiliations:
      - id: id1
        name: "University of Chicago"
        group: Psychology
        department: MAPSS
        address: 1155 E 60th street
        city: Chicago
        state: Illinois 
        country: USA
        postal-code: 60637
author-note:
  disclosures:
    conflict-of-interest: The authors have no conflicts of interest to disclose.
    gratitude: "I would like to thank Dr. Onnie Rogers, the prinicpal investigator of TeenTee and Dr. Natalie Dowling for helping me in the coding of the project." 
abstract: "Black girls often face unique challenges due to the intersecting forms of oppression they face, thus requiring targeted support to navigate these barriers and promote their well-being. The Teen TEE (Talk, Educate, Experience) program is a strengths-based initiative aimed at empowering early adolescent Black girls by fostering identity development, belonging, and community building. The current study evaluates the effectiveness of the Teen TEE program by comparing pre- and post-intervention results on 10 key constructs i.e. Empathy and Sympathy (Ames), Self-Compassion, Emotional Clarity, Self-Esteem, Black Girl Identity, Image Acceptance, Relatedness, Belongingness, Black Girl Space, and Critical Agency. Findings reveal a significant increase in belonging and the creation of supportive Black girl spaces pre and post intervention, while no other scales showed significant changes."
keywords: [Black girls, Intersectionality, Identity development, Belongingness, Black Girl Space]
floatsintext: true
numbered-lines: false
bibliography: "teentee.bib"
suppress-title-page: false
link-citations: true
mask: false
draft-date: false
lang: en
language:
  email: "Email"
  title-block-correspondence-note: "Correspondence concerning this article should be addressed to"
format:
  apaquarto-docx: 
    default: true
    warning: false  
    message: false
  apaquarto-html: default
  apaquarto-typst: 
    keep-typ: true
    toc: true
  apaquarto-pdf:
    documentmode: man
    dontrepeattitle: false
    suppress-title-introduction: false
execute:
  warning: false
---

```{r}
#| label: setup
#| include: false

#install packages
# install.packages("conflicted")
# install.packages("tidyverse")
# install.packages("flextable")
# install.packages("ftExtra")
# install.packages("knitr")
# install.packages("gridExtra")
# install.packages("forcats")

#load oackages
library(conflicted)
library(tidyverse)
library(flextable)
library(ftExtra)
library(knitr)
library(gridExtra)
library(forcats)
conflicts_prefer(dplyr::filter, .quiet = TRUE)
conflicts_prefer(flextable::separate_header, .quiet = TRUE)
```

Being a youth in today's world is not easy. According to @erikson_identity_1968, Adolescence is a critical and vulnerable stage of development, shaping an individual’s identity, sense of belonging, and future opportunities. In order to thrive, young people need access to sufficient support that can help mitigate the risks and challenges they face while growing up [@hope_civic_2017].

However, in a society structured by layers of intersectional oppression, the support-to-risk ratio is not equal for all youth. This imbalance is particularly pronounced for Black girls, whose experiences are often compounded by societal bias and systemic inequities [@crenshaw_black_2015]. For example, by the age of 5, Black girls are perceived as more "adult-like" than their same-aged peers, a phenomenon known as adultification bias [@gonzalez_classroom_2018. This bias magnifies their vulnerability to sexual harassment, harsher disciplinary measures in schools, and long-term psychological and educational challenges [@gonzalez_classroom_2018; @morris_vocational_2016]. This systemic marginalization demands intentional and transformative efforts to reimagine the kinds of support Black girls need, focusing on strengths-based initiatives that address their lived realities and nurture their holistic well-being.

The Teen TEE (Talk, Educate, Experience) [^1] program is an evidence-based initiative designed to support early adolescent Black girls by fostering a positive environment where they can develop healthy relationships, strong identities, and a sense of community. This strengths-based program provides a space for Black girls to engage in open dialogue, gain education on relevant topics, and participate in hands-on experiences that help them navigate the unique challenges they face. The program aims to create an affirming and empowering space where participants can explore their identities, learn about their cultural heritage, and build resilience in the face of societal pressures.

[^1]: project started by Dr. Onnie Rogers and Gloria Dotson-Lewis

**The current study** evaluates the efficacy of the Teen TEE program in promoting key outcomes for Black girls, including increased self-esteem, a stronger sense of Black girl identity, and a greater sense of belonging. Specifically, the project looks at how participation in the program influences the development of positive self-concept, the creation of supportive Black girl spaces, and the overall enhancement of belongingness in a society that often marginalizes them. Through this assessment, the project seeks to determine the program’s impact on the personal growth and well-being of Black girls, helping to inform future initiatives that support their empowerment and development.


## Hypotheses
The current study aims to evaluate the impact of the Teen TEE program in promoting key outcomes among early adolescent Black girls. Specifically, the study focuses on 10 constructs: Empathy and Symapthy, Self Compassion, Emotional Clarity, Self Esteem, Black Girl Identity, Image Acceptance, Relatedness, Belongingness, Black Girl Space, and Critical Agency. Each construct represents an important aspect of identity, social well-being, and personal growth for the participants. For each construct, the following hypotheses are proposed:

- Null Hypothesis (H₀): There is no significant difference in pre- and post-intervention scores for each construct.
- Alternative Hypothesis (H₁): There is a significant difference in pre- and post-intervention scores for each construct.


\newpage

# Methodology

## Sample
The study sample consists of 15 Black girls, aged 11-14 years old (6th-8th grade), who participated in the Teen TEE (Talk, Educate, Experience) program. Data was collected during the 2023-2024 academic year across two program cycles (Spring and Fall). Participation was voluntary, and parental consent and youth assent were obtained. The study was conducted in a school setting, with program sessions held after school hours. To support engagement, participants were provided with snacks during each session.

## Study Design & Measures
This study employs a pre-post intervention design to assess changes in key psychological and identity-related constructs before and after participation in the Teen TEE program. Each participant completed self-report measures at two time points: before (pre) and after (post) the program. Data collection occurred across both program cycles, capturing changes in participant outcomes over the course of the intervention.

To ensure the measures were relevant to the experiences of Black girls, full standardized scales were not used. Instead, selected items from ten established psychological measures were adapted to create a customized assessment tool. This tool included questions specifically relevant to Black girl identity, self-concept, and belonging, forming a structured interview schedule tailored to the study’s objectives. The constructs assessed included:

1. Empathy and Sympathy (items adapted from the Adolescent Measure of Empathy and Sympathy (AMES) by @vossen_development_2015)
2. Self Compassion (items adapted from the Self-Compassion Scale Youth Version by @neff_development_2021)
3. Emotional Clarity (items created for Teen TEE)
4. Self Esteem (items adapted from the Rosenberg Self-Esteem scale by @rosenberg_rosenberg_1965)
5. Black Girl Identity (items adapted from the ERI measure of identity exploration and resolution by @umana-taylor_developing_2004)
6. Image Acceptance (items adapted from the Image Acceptance Measure (I AM) colorism scale by @plybon_image_2003)
7. Relatedness (items adapted from The Youth Relatedness Scale by @deloia_youth_2012)
8. Belonging (items adapted from the Simple School Belonging Scale (SSBS) by @whiting_simple_2018)
9. Black Girl Space (items created for Teen TEE)
10. Critical Agency (items adapted from the Measure of Adolescent Critical Consciousness (MACC) scale by @mcwhirter_critical_nodate)

This approach ensured that the assessment was both culturally responsive and developmentally appropriate for the participants, aligning with the unique experiences of Black girls and the goals of the Teen TEE program.

## Procedure
Participants completed the pre-intervention survey at the beginning of the program. The Teen TEE program ran for a specified 10-week duration, incorporating discussions, educational sessions, and experiential activities. Upon program completion, participants completed the post-intervention survey to assess changes in the measured constructs. Data was collected in paper format and then entered in Qualtrics by research assistants.

\newpage

# Results & Discussion

The data was collected and scored according to the scoring manual of scales applied. The responses were analysed using paired T-Test to analyse and asses the pre and post scores of different scales. The tables and plots below indicate the findings. 


Table 1: Paired T-Test Results for Key Constructs

```{r}
#| label: tbl-results1
#| message: false

# read in data
results_data <- read_csv("results_data")
results_data$"Pre Mean" <- round(results_data$"Pre Mean", 2)
results_data$"Post Mean" <- round(results_data$"Post Mean", 2)

results_data$Significance <- format(round(results_data$Significance, 3), nsmall = 3)

#presenting as table
results_data1 <- results_data %>% 
  flextable() %>% 
  flextable::theme_apa()

results_data1
```


\newpage
*Plot 1:* 

```{r}
#| label: Figure1
#| warning: false

#install package
## install.packages(ggplot2)

#load package
library(ggplot2)

tidy.data <- read.csv("tidy_data.csv")

ames1 <- ggplot(tidy.data, aes(x= Time,
                      y= Ames))+
  geom_boxplot()+
  geom_point(aes(color = as.factor(Name)))+
  theme_minimal() + 
  labs(color = "Participant ID", 
       x = "Time", 
       y = "Ames Score") +
  scale_x_discrete(limits = c("Pre", "Post"))+
  guides(color = "none")+
  theme(axis.title = element_text(face = "italic"),
        plot.title = element_text(face = "italic"))

ames2 <- ggplot(tidy.data, aes(x = Time, 
                      y = Ames, 
                      group = Name, 
                      color = as.factor(Name))) + 
  geom_point(size = 3) +   # Scatter plot points
  geom_line(size = 1, alpha = 0.7) +  # Lines connecting points for each participant
  theme_minimal() + 
  labs(color = "Participant ID", 
       x = "Time", 
       y = "Ames Score") +
  scale_x_discrete(limits = c("Pre", "Post"))+
  theme(axis.title = element_text(face = "italic"),
        plot.title = element_text(face = "italic"))

grid.arrange(ames1, ames2, ncol= 2, 
             top = "Pre & Post Ames Scores")
```
**For the construct of Empathy and Sympathy (Ames),** it was found that the mean scores `r if (results_data$"Post Mean"[results_data$Scale == "Ames"] > results_data$"Pre Mean"[results_data$Scale == "Ames"]) "increased" else "decreased"` following the Teen TEE intervention (Pre = `r results_data$"Pre Mean"[results_data$Scale == "Ames"]` and Post = `r results_data$"Post Mean"[results_data$Scale == "Ames"]`). To assess whether this change was statistically significant, a paired t-test was conducted comparing the pre and post-intervention score, and significance values was calculated. (p = `r results_data$"Significance"[results_data$Scale == "Ames"]`). Since the p-value is `r if(results_data$"Significance"[results_data$Scale == "Ames"] < 0.05) "less than" else "greater than"` than 0.05, i.e. the results are `r if(results_data$"Significance"[results_data$Scale == "Ames"] < 0.05) "statistically significant" else "not significant"`. Therefore, the null hypothesis is `r if(results_data$"Significance"[results_data$Scale == "Ames"] < 0.05) "rejected and it is found that there is a meaningful improvement" else "accepted and there is no meaningful improvement "` in the scores as a result of the intervention.


\newpage
*Plot 2:*
```{r}
#| label: GGPlot Self Compassion Scale
#| warning: false

SelfComp1 <- ggplot(tidy.data, aes(x= Time,
                      y= SelfCompassion))+
  geom_boxplot()+
  geom_point(aes(color = as.factor(Name)))+
  theme_minimal() + 
  labs(color = "Participant ID", 
       x = "Time", 
       y = "Self Compassion Score") +
  scale_x_discrete(limits = c("Pre", "Post"))+
  guides(color = "none")+
  theme(axis.title = element_text(face = "italic"),
        plot.title = element_text(face = "italic"))

SelfComp2 <- ggplot(tidy.data, aes(x = Time, 
                      y = SelfCompassion, 
                      group = Name, 
                      color = as.factor(Name))) + 
  geom_point(size = 3) +   
  geom_line(size = 1, alpha = 0.7) + 
  theme_minimal() + 
  labs(color = "Participant ID", 
       x = "Time", 
       y = "Self Compassion Score") +
  scale_x_discrete(limits = c("Pre", "Post"))+
  theme(axis.title = element_text(face = "italic"),
        plot.title = element_text(face = "italic"))

grid.arrange(SelfComp1, SelfComp2, ncol= 2, 
             top = "Pre & Post Self Compassion Scores")
```
**For the construct of Self Compassion,** it was found that the mean scores `r if (results_data$"Post Mean"[results_data$Scale == "Self Compassion"] > results_data$"Pre Mean"[results_data$Scale == "Self Compassion"]) "increased" else "decreased"` following the Teen TEE intervention (Pre = `r results_data$"Pre Mean"[results_data$Scale == "Self Compassion"]` and Post = `r results_data$"Post Mean"[results_data$Scale == "Self Compassion"]`). To assess whether this change was statistically significant, a paired t-test was conducted comparing the pre and post-intervention scores, and significance values were calculated. (p = `r results_data$"Significance"[results_data$Scale == "Self Compassion"]`). Since the p-value is `r if(results_data$"Significance"[results_data$Scale == "Self Compassion"] < 0.05) "less than" else "greater than"` than 0.05, i.e. the results are `r if(results_data$"Significance"[results_data$Scale == "Self Compassion"] < 0.05) "statistically significant" else "not significant"`. Therefore, the null hypothesis is `r if(results_data$"Significance"[results_data$Scale == "Self Compassion"] < 0.05) "rejected and it is found that there is a meaningful improvement" else "accepted and there is no meaningful improvement "` in the scores as a result of the intervention.



\newpage
*Plot 3:*

```{r}
#| label: GGPlot Emotional Clarity Scale
#| warning: false

# Box plot for EmoClarity scores
emoClarity1 <- ggplot(tidy.data, aes(x = Time,
                                     y = EmoClarity)) +
  geom_boxplot() +
  geom_point(aes(color = as.factor(Name))) +
  theme_minimal() + 
  labs(color = "Participant ID", 
       x = "Time", 
       y = "EmoClarity Score") +
  scale_x_discrete(limits = c("Pre", "Post"))+
  guides(color = "none")+
  theme(axis.title = element_text(face = "italic"),
        plot.title = element_text(face = "italic"))

# Scatter + Line plot for EmoClarity scores
emoClarity2 <- ggplot(tidy.data, aes(x = Time, 
                                     y = EmoClarity, 
                                     group = Name, 
                                     color = as.factor(Name))) + 
  geom_point(size = 3) +   
  geom_line(size = 1, alpha = 0.7) + 
  theme_minimal() + 
  labs(color = "Participant ID", 
       x = "Time", 
       y = "EmoClarity Score") +
  scale_x_discrete(limits = c("Pre", "Post"))+
  theme(axis.title = element_text(face = "italic"),
        plot.title = element_text(face = "italic"))

# Display both plots side by side
grid.arrange(emoClarity1, emoClarity2, ncol = 2, 
             top = "Pre & Post Emotional Clarity Scores")
```
**For the construct of Emotional Clarity,** it was found that the mean scores `r if (results_data$"Post Mean"[results_data$Scale == "Emo Clarity"] > results_data$"Pre Mean"[results_data$Scale == "Emo Clarity"]) "increased" else "decreased"` following the Teen TEE intervention (Pre = `r results_data$"Pre Mean"[results_data$Scale == "Emo Clarity"]` and Post = `r results_data$"Post Mean"[results_data$Scale == "Emo Clarity"]`). To assess whether this change was statistically significant, a paired t-test was conducted comparing the pre and post-intervention scores, and significance values were calculated. (p = `r results_data$"Significance"[results_data$Scale == "Emo Clarity"]`). Since the p-value is `r if(results_data$"Significance"[results_data$Scale == "Emo Clarity"] < 0.05) "less than" else "greater than"` than 0.05, i.e. the results are `r if(results_data$"Significance"[results_data$Scale == "Emo Clarity"] < 0.05) "statistically significant" else "not significant"`. Therefore, the null hypothesis is `r if(results_data$"Significance"[results_data$Scale == "Emo Clarity"] < 0.05) "rejected and it is found that there is a meaningful improvement" else "accepted and there is no meaningful improvement "` in the scores as a result of the intervention.


\newpage
*Plot 4:*
```{r}
#| label: GGPlot Self Esteem scores Scale
#| warning: false

# Box plot for Self Esteem scores
selfEsteem1 <- ggplot(tidy.data, aes(x = Time,
                                     y = SelfEsteem)) +
  geom_boxplot() +
  geom_point(aes(color = as.factor(Name))) +
  theme_minimal() + 
  labs(color = "Participant ID", 
       x = "Time", 
       y = "SelfEsteem Score") +
  scale_x_discrete(limits = c("Pre", "Post"))+
  guides(color = "none")+
  theme(axis.title = element_text(face = "italic"),
        plot.title = element_text(face = "italic"))

# Scatter + Line plot for SelfEsteem scores
selfEsteem2 <- ggplot(tidy.data, aes(x = Time, 
                                     y = SelfEsteem, 
                                     group = Name, 
                                     color = as.factor(Name))) + 
  geom_point(size = 3) +   # Scatter plot points
  geom_line(size = 1, alpha = 0.7) +  # Lines connecting points for each participant
  theme_minimal() + 
  labs(color = "Participant ID", 
       x = "Time", 
       y = "SelfEsteem Score") +
  scale_x_discrete(limits = c("Pre", "Post"))+
  theme(axis.title = element_text(face = "italic"),
        plot.title = element_text(face = "italic"))

# Display both plots side by side
grid.arrange(selfEsteem1, selfEsteem2, ncol = 2, 
             top = "Pre & Post Self Esteem Scores")

```

**For the construct of "Self Esteem" (Ames),** it was found that the mean scores `r if (results_data$"Post Mean"[results_data$Scale == "Self Esteem"] > results_data$"Pre Mean"[results_data$Scale == "Self Esteem"]) "increased" else "decreased"` following the Teen TEE intervention (Pre = `r results_data$"Pre Mean"[results_data$Scale == "Self Esteem"]` and Post = `r results_data$"Post Mean"[results_data$Scale == "Self Esteem"]`). To assess whether this change was statistically significant, a paired t-test was conducted comparing the pre and post-intervention score, and significance values were calculated (p = `r results_data$"Significance"[results_data$Scale == "Self Esteem"]`). Since the p-value is `r if(results_data$"Significance"[results_data$Scale == "Self Esteem"] < 0.05) "less than" else "greater than"` than 0.05, i.e., the results are `r if(results_data$"Significance"[results_data$Scale == "Self Esteem"] < 0.05) "statistically significant" else "not significant"`. Therefore, the null hypothesis is `r if(results_data$"Significance"[results_data$Scale == "Self Esteem"] < 0.05) "rejected and it is found that there is a meaningful improvement" else "accepted and there is no meaningful improvement "` in the scores as a result of the intervention.


\newpage
*Plot 5: *

```{r}
#| label: GGPlot Black Girl Id scores Scale
#| warning: false

# Box plot for Blackgirl ID scores
BG1 <- ggplot(tidy.data, aes(x = Time,
                                       y = BlackGirlId)) +
  geom_boxplot() +
  geom_point(aes(color = as.factor(Name))) +
  theme_minimal() + 
  labs(color = "Participant ID", 
       x = "Time", 
       y = "Blackgirl ID Score") +
  scale_x_discrete(limits = c("Pre", "Post"))+
  guides(color = "none")+
  theme(axis.title = element_text(face = "italic"),
        plot.title = element_text(face = "italic"))

# Scatter + Line plot for Blackgirl ID scores
BG2 <- ggplot(tidy.data, aes(x = Time, 
                                       y = BlackGirlId, 
                                       group = Name, 
                                       color = as.factor(Name))) + 
  geom_point(size = 3) +   
  geom_line(size = 1, alpha = 0.7) + 
  theme_minimal() + 
  labs(color = "Participant ID", 
       x = "Time", 
       y = "Blackgirl ID Score") +
  scale_x_discrete(limits = c("Pre", "Post"))+
  theme(axis.title = element_text(face = "italic"),
        plot.title = element_text(face = "italic"))

# Display both plots side by side
grid.arrange(BG1, BG2, ncol = 2, 
             top = "Pre & Post Black Girl Id Scores")
```
**For the construct of "Black Girl Id" (Ames),** it was found that the mean scores `r if (results_data$"Post Mean"[results_data$Scale == "Black Girl Id"] > results_data$"Pre Mean"[results_data$Scale == "Black Girl Id"]) "increased" else "decreased"` following the Teen TEE intervention (Pre = `r results_data$"Pre Mean"[results_data$Scale == "Black Girl Id"]` and Post = `r results_data$"Post Mean"[results_data$Scale == "Black Girl Id"]`). To assess whether this change was statistically significant, a paired t-test was conducted comparing the pre and post-intervention score, and significance values were calculated (p = `r results_data$"Significance"[results_data$Scale == "Black Girl Id"]`). Since the p-value is `r if(results_data$"Significance"[results_data$Scale == "Black Girl Id"] < 0.05) "less than" else "greater than"` than 0.05, i.e., the results are `r if(results_data$"Significance"[results_data$Scale == "Black Girl Id"] < 0.05) "statistically significant" else "not significant"`. Therefore, the null hypothesis is `r if(results_data$"Significance"[results_data$Scale == "Black Girl Id"] < 0.05) "rejected and it is found that there is a meaningful improvement" else "accepted and there is no meaningful improvement "` in the scores as a result of the  intervention.



\newpage
*Plot 6:*
```{r}
#| label: GGPlot Img Acceptance scores Scale
#| warning: false

# Box plot for ImgAcceptance scores
img_acceptance1 <- ggplot(tidy.data, aes(x = Time,
                                         y = ImgAcceptance)) +
  geom_boxplot() +
  geom_point(aes(color = as.factor(Name))) +
  theme_minimal() + 
  labs(color = "Participant ID", 
       x = "Time", 
       y = "ImgAcceptance Score") +
  scale_x_discrete(limits = c("Pre", "Post"))+
  guides(color = "none")+
  theme(axis.title = element_text(face = "italic"),
        plot.title = element_text(face = "italic"))

# Scatter + Line plot for ImgAcceptance scores
img_acceptance2 <- ggplot(tidy.data, aes(x = Time, 
                                         y = ImgAcceptance, 
                                         group = Name, 
                                         color = as.factor(Name))) + 
  geom_point(size = 3) +  
  geom_line(size = 1, alpha = 0.7) +  
  theme_minimal() + 
  labs(color = "Participant ID", 
       x = "Time", 
       y = "ImgAcceptance Score") +
  scale_x_discrete(limits = c("Pre", "Post"))+
  theme(axis.title = element_text(face = "italic"),
        plot.title = element_text(face = "italic"))

# Display both plots side by side
grid.arrange(img_acceptance1, img_acceptance2, ncol = 2, 
             top = "Pre & Post Image Acceptance Scores")

```

**For the construct of Image Acceptance,** it was found that the mean scores `r if (results_data$"Post Mean"[results_data$Scale == "Img Acceptance"] > results_data$"Pre Mean"[results_data$Scale == "Img Acceptance"]) "increased" else "decreased"` following the Teen TEE intervention (Pre = `r results_data$"Pre Mean"[results_data$Scale == "Img Acceptance"]` and Post = `r results_data$"Post Mean"[results_data$Scale == "Img Acceptance"]`). To assess whether this change was statistically significant, a paired t-test was conducted comparing the pre and post-intervention score, and significance values were calculated. (p = `r results_data$"Significance"[results_data$Scale == "Img Acceptance"]`). Since the p-value is `r if(results_data$"Significance"[results_data$Scale == "Img Acceptance"] < 0.05) "less than" else "greater than"` than 0.05, i.e., the results are `r if(results_data$"Significance"[results_data$Scale == "Img Acceptance"] < 0.05) "statistically significant" else "not significant"`. Therefore, the null hypothesis is `r if(results_data$"Significance"[results_data$Scale == "Img Acceptance"] < 0.05) "rejected and it is found that there is a meaningful improvement" else "accepted and there is no meaningful improvement "` in the scores as a result of the intervention.


\newpage
*Plot 7:*
```{r}
#| label: GGPlot Relatedness scores Scale
#| warning: false

# Box plot for Relatedness scores
relatedness1 <- ggplot(tidy.data, aes(x = Time,
                                      y = Relatedness)) +
  geom_boxplot() +
  geom_point(aes(color = as.factor(Name))) +
  theme_minimal() + 
  labs(color = "Participant ID", 
       x = "Time", 
       y = "Relatedness Score") +
  scale_x_discrete(limits = c("Pre", "Post"))+
  guides(color = "none")+
  theme(axis.title = element_text(face = "italic"),
        plot.title = element_text(face = "italic"))

# Scatter + Line plot for Relatedness scores
relatedness2 <- ggplot(tidy.data, aes(x = Time, 
                                      y = Relatedness, 
                                      group = Name, 
                                      color = as.factor(Name))) + 
  geom_point(size = 3) +   
  geom_line(size = 1, alpha = 0.7) +  
  theme_minimal() + 
  labs(color = "Participant ID", 
       x = "Time", 
       y = "Relatedness Score") +
  scale_x_discrete(limits = c("Pre", "Post"))+
  theme(axis.title = element_text(face = "italic"),
        plot.title = element_text(face = "italic"))

# Display both plots side by side
grid.arrange(relatedness1, relatedness2, ncol = 2, 
             top = "Pre & Post Relatedness Scores")
```
**For the construct of Relatedness,** it was found that the mean scores `r if (results_data$"Post Mean"[results_data$Scale == "Relatedness"] > results_data$"Pre Mean"[results_data$Scale == "Relatedness"]) "increased" else "decreased"` following the Teen TEE intervention (Pre = `r results_data$"Pre Mean"[results_data$Scale == "Relatedness"]` and Post = `r results_data$"Post Mean"[results_data$Scale == "Relatedness"]`). To assess whether this change was statistically significant, a paired t-test was conducted comparing the pre and post-intervention score, and significance values were calculated. (p = `r results_data$"Significance"[results_data$Scale == "Relatedness"]`). Since the p-value is `r if(results_data$"Significance"[results_data$Scale == "Relatedness"] < 0.05) "less than" else "greater than"` than 0.05, i.e., the results are `r if(results_data$"Significance"[results_data$Scale == "Relatedness"] < 0.05) "statistically significant" else "not significant"`. Therefore, the null hypothesis is `r if(results_data$"Significance"[results_data$Scale == "Relatedness"] < 0.05) "rejected and it is found that there is a meaningful improvement" else "accepted and there is no meaningful improvement "` in the scores as a result of the intervention.

\newpage
*Plot 8:*
```{r}
#| label: GGPlot Belonging scores Scale
#| warning: false

# Box plot for Belonging scores
belonging1 <- ggplot(tidy.data, aes(x = Time,
                                    y = Belonging)) +
  geom_boxplot() +
  geom_point(aes(color = as.factor(Name))) +
  theme_minimal() + 
  labs(color = "Participant ID", 
       x = "Time", 
       y = "Belonging Score") +
  scale_x_discrete(limits = c("Pre", "Post"))+
  guides(color = "none")+
  theme(axis.title = element_text(face = "italic"),
        plot.title = element_text(face = "italic"))

# Scatter + Line plot for Belonging scores
belonging2 <- ggplot(tidy.data, aes(x = Time, 
                                    y = Belonging, 
                                    group = Name, 
                                    color = as.factor(Name))) + 
  geom_point(size = 3) +   
  geom_line(size = 1, alpha = 0.7) +  
  theme_minimal() + 
  labs(color = "Participant ID", 
       x = "Time", 
       y = "Belonging Score") +
  scale_x_discrete(limits = c("Pre", "Post"))+
  theme(axis.title = element_text(face = "italic"),
        plot.title = element_text(face = "italic"))

# Display both plots side by side
grid.arrange(belonging1, belonging2, ncol = 2, 
             top = "Pre & Post Belonging Scores")
```

**For the construct of Belonging,** it was found that the mean scores `r if (results_data$"Post Mean"[results_data$Scale == "Belonging"] > results_data$"Pre Mean"[results_data$Scale == "Belonging"]) "increased" else "decreased"` following the Teen TEE intervention (Pre = `r results_data$"Pre Mean"[results_data$Scale == "Belonging"]` and Post = `r results_data$"Post Mean"[results_data$Scale == "Belonging"]`). To assess whether this change was statistically significant, a paired t-test was conducted comparing the pre and post-intervention score, and significance values were calculated. (p = `r results_data$"Significance"[results_data$Scale == "Belonging"]`). Since the p-value is `r if(results_data$"Significance"[results_data$Scale == "Belonging"] < 0.05) "less than" else "greater than"` than 0.05, i.e. the results are `r if(results_data$"Significance"[results_data$Scale == "Belonging"] < 0.05) "statistically significant" else "not significant"`. Therefore, the null hypothesis is `r if(results_data$"Significance"[results_data$Scale == "Belonging"] < 0.05) "rejected and it is found that there is a meaningful improvement" else "accepted and there is no meaningful improvement "` in the scores as a result of the intervention.


\newpage
*Plot 9:*
```{r}
#| label: GGPlot Black Girl Space scores Scale
#| warning: false

# Box plot for BlackGirl Space scores
blackgirl_space1 <- ggplot(tidy.data, aes(x = Time,
                                          y = BlackGirlSpace)) +
  geom_boxplot() +
  geom_point(aes(color = as.factor(Name))) +
  theme_minimal() + 
  labs(color = "Participant ID", 
       x = "Time", 
       y = "BlackGirl Space Score") +
  scale_x_discrete(limits = c("Pre", "Post"))+
  guides(color = "none") +
  theme(axis.title = element_text(face = "italic"),
        plot.title = element_text(face = "italic"))

# Scatter + Line plot for BlackGirl Space scores
blackgirl_space2 <- ggplot(tidy.data, aes(x = Time, 
                                          y = BlackGirlSpace, 
                                          group = Name, 
                                          color = as.factor(Name))) + 
  geom_point(size = 3) +  
  geom_line(size = 1, alpha = 0.7) + 
  theme_minimal() + 
  labs(color = "Participant ID", 
       x = "Time", 
       y = "BlackGirl Space Score") +
  scale_x_discrete(limits = c("Pre", "Post"))+
  theme(axis.title = element_text(face = "italic"),
        plot.title = element_text(face = "italic"))

# Display both plots side by side
grid.arrange(blackgirl_space1, blackgirl_space2, ncol = 2, 
             top = "Pre & Post Black Girl Space Scores")
```
**For the construct of Black Girl Space,** it was found that the mean scores `r if (results_data$"Post Mean"[results_data$Scale == "Black Girl Space"] > results_data$"Pre Mean"[results_data$Scale == "Black Girl Space"]) "increased" else "decreased"` following the Teen TEE intervention (Pre = `r results_data$"Pre Mean"[results_data$Scale == "Black Girl Space"]` and Post = `r results_data$"Post Mean"[results_data$Scale == "Black Girl Space"]`). To assess whether this change was statistically significant, a paired t-test was conducted comparing the pre and post-intervention score, and significance values were calculated. (p = `r results_data$"Significance"[results_data$Scale == "Black Girl Space"]`). Since the p-value is `r if(results_data$"Significance"[results_data$Scale == "Black Girl Space"] < 0.05) "less than" else "greater than"` than 0.05, i.e. the results are `r if(results_data$"Significance"[results_data$Scale == "Black Girl Space"] < 0.05) "statistically significant" else "not significant"`. Therefore, the null hypothesis is `r if(results_data$"Significance"[results_data$Scale == "Black Girl Space"] < 0.05) "rejected and it is found that there is a meaningful improvement" else "accepted and there is no meaningful improvement "` in the scores as a result of the intervention.


\newpage
*Plot 10:*
```{r}
#| label: GGPlot Critical Agency scores Scale
#| warning: false

# Box plot for Critical Agency scores
critical_agency1 <- ggplot(tidy.data, aes(x = Time,
                                          y = CriticalAgency)) +
  geom_boxplot() +
  geom_point(aes(color = as.factor(Name))) +
  theme_minimal() + 
  labs(color = "Participant ID", 
       x = "Time", 
       y = "Critical Agency Score") +
  scale_x_discrete(limits = c("Pre", "Post"))+
  guides(color = "none")+
  theme(axis.title = element_text(face = "italic"),
        plot.title = element_text(face = "italic"))

# Scatter + Line plot for Critical Agency scores
critical_agency2 <- ggplot(tidy.data, aes(x = Time, 
                                          y = CriticalAgency, 
                                          group = Name, 
                                          color = as.factor(Name))) + 
  geom_point(size = 3) +   
  geom_line(size = 1, alpha = 0.7) +  
  theme_minimal() + 
  labs(color = "Participant ID", 
       x = "Time", 
       y = "Critical Agency Score") +
  scale_x_discrete(limits = c("Pre", "Post"))+
  theme(axis.title = element_text(face = "italic"),
        plot.title = element_text(face = "italic"))

# Display both plots side by side
grid.arrange(critical_agency1, critical_agency2, ncol = 2, 
             top = "Pre & Post Critical Agency Scores")
```


**For the construct of Critical Agency,** it was found that the mean scores `r if (results_data$"Post Mean"[results_data$Scale == "Critical Agency"] > results_data$"Pre Mean"[results_data$Scale == "Critical Agency"]) "increased" else "decreased"` following the Teen TEE intervention (Pre = `r results_data$"Pre Mean"[results_data$Scale == "Critical Agency"]` and Post = `r results_data$"Post Mean"[results_data$Scale == "Critical Agency"]`). To assess whether this change was statistically significant, a paired t-test was conducted comparing the pre and post-intervention score, and significance values were calculated (p = `r results_data$"Significance"[results_data$Scale == "Critical Agency"]`). Since the p-value is `r if(results_data$"Significance"[results_data$Scale == "Critical Agency"] < 0.05) "less than" else "greater than"` than 0.05, i.e. the results are `r if(results_data$"Significance"[results_data$Scale == "Critical Agency"] < 0.05) "statistically significant" else "not significant"`. Therefore, the null hypothesis is `r if(results_data$"Significance"[results_data$Scale == "Critical Agency"] < 0.05) "rejected and it is found that there is a meaningful improvement" else "accepted and there is no meaningful improvement "` in the scores as a result of the intervention.


 

## Conclusion
The current study wanted to look at the impact of strength based programs such as Teen TEE on several psychological and identity-related constructs among Black girls. For the chosen 10 constructs, scores were collected pre and post intervention. As @tbl-results1 shows, that although there was a positive increase in all constructs, only two had significant differences i.e **Belonging** and **Black Girl Space**. This suggests that the program significantly fostered a stronger sense of community and affirmation among participants.

```{r}
#| label: Facet Wrap

results_long <- results_data %>%
  pivot_longer(
    cols = c("Pre Mean", "Post Mean"),
    names_to = "Time",
    values_to = "MeanScore"
  ) %>%
  mutate(Time = as.factor(Time)) %>%
  mutate(Time = fct_relevel(Time, "Pre Mean", "Post Mean")) %>% 
  mutate(Time = fct_recode(Time, "Pre Avg" = "Pre Mean", "Post Avg" = "Post Mean"))
  

# Create the faceted plot
ggplot(results_long, aes(x = Time, y = MeanScore, fill = Time)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_wrap(~ Scale, scales = "free_y", nrow = 2) +
  labs(title = "Pre and Post Mean Scores by Scale",
       x = "Time",
       y = "Mean Score",
       fill = "Time") +
  theme_minimal()+
  scale_x_discrete(labels = NULL) +
  scale_fill_manual(values = c("Pre Avg" = "pink", "Post Avg" = "lightblue")) +
  theme(
    plot.title = element_text(face = "bold"),   
    axis.title.x = element_text(face = "bold"),  
    axis.title.y = element_text(face = "bold"))

```

However, most constructs showed no significant differences. This could be because of several limiations which should be considered when interpreting the results of this study. First, most constructs showed no significant differences, which could be attributed to the small sample size. A larger sample would provide more reliable data and better insights into the effectiveness of the Teen TEE program. Second, the reliance on quantitative data may not fully capture the complexity of the constructs being assessed. Incorporating qualitative methods, such as interviews, could provide a more comprehensive understanding of how these constructs are experienced and enhanced in the participants' lives. Additionally, the constructs were not fully assessed: questions were handpicked to suit the needs which could affect the validity and reliability of the constructs.  

Despite these limitations, the results highlight the importance of tailored, strengths-based approaches that address the unique challenges faced by Black girls and underscore the potential of community-building initiatives in promoting positive identity development and resilience. Future research should aim to enhance the program's impact on personal constructs and explore its long-term effects. [^2]

[^2]:This conclusion is based on the findings of the current study. If future results differ, the conclusion should be revised accordingly. 



\newpage
# References


::: {#refs}
:::

# Appendix


